
\documentclass{article}

\usepackage{fullpage,latexsym,picinpar,amsmath,amsfonts}

\input{macros.tex}

\begin{document}

\centerline{\large \bf CS/MATH111 SUNTINWONG! ASSIGNMENT 1}
\centerline{due Tuesday, April 12}

\vskip 0.1in
\noindent{\bf Individual assignment:} Problems 1 and 2.

\noindent{\bf Group assignment:} Problems 1,2 and 3.

\vskip 0.2in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{problem}
(a)
Give the exact formula (as a function of $n$) for the number of
times ``whatsup" is printed by Algorithm~\textsc{WhatsUp} below.
First express it as a summation, and then give a closed-form expression.

\noindent
(b)
Give the asymptotic value of the
number of ``whatsup"s (using the $\Theta$-notation.)

\begin{tabbing}
aa \= aa \= aa \= aa \= aa \= aa \= \kill
\textbf{Algorithm} \textsc{WhatsUp} $(n: \mbox{\bf integer})$ \\
      \> \textbf{for} $i \leftarrow 1$ \textbf{to} $2n$
                         \textbf{do} \\
      \> \> \textbf{for} $j \leftarrow 1$ \textbf{to} $(i+1)^2$ \textbf{do} \\
      \> \> \> print(``whatsup")
\end{tabbing}
\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{problem}
Let $f(n)$ be a function on natural numbers defined
recursively by $f(0) = 1$, $f(1) = 2.3$, $f(n+2) = 3f(n) + f(n+1)$.
Prove by induction that
$(9/4)^n \le f(n) \le (7/3)^n$.
\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{problem}
Give as good big-O estimates as possible for the
following functions:
%
\begin{description}
%
\item{(a)} $3n^2 + 7 n^4 + n + 17$
\item{(b)} $n^3 (n\log n + \sqrt{n}+5 )$
\item{(c)} $n^3\log^3n + 13 n^2\log^5n + n^{1.5}$
\item{(d)} $n^3 + n^2 4^n + \log^5 n$
\item{(e)} $n3^n + 5^n$
%
\end{description}
%
Justify your answer.
(Here, you don't need to give a complete rigorous proof.
Give only an informal explanation using asymptotic
relations between the functions $n^c$, $\log n$, and
$c^n$.)
\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 0.1in
\paragraph{Submission.}
You need to turn in your homework by Tuesday, April 12 (midnight).
Submit the homework in Ilearn in the pdf format.

\paragraph{Reminders.}
Remember that only {\LaTeX} papers are accepted. Also,
remember to turn in your signed academic integrity statement.

\end{document}

